Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/memo2_TAS_reviewers.Rmd
additions to reviewer memo

We have revised accordingly. [TBD]

@@

@@

TBD

@@

As we discuss in the paper (page X, lines YY-YY), how one chooses the subsetting criteria (e.g., "similar" cases) would have to be justified with respect to its _assumed_ effect on the degree of compatability between the historical trials and the current trial ($b_hist - $b_curr$). We stress _assumed_, because outside simulations like ours, neither $b_hist$ nor $b_curr$ are directly observable in actual cases. Accordingly, for any subset of the historical strike data one chooses, our guidance for choosing an $\alpha$ value remains the same: Check for how sensitive to the posterior estimate of strike bias to different values of $\alpha$.  The current version of the software prototype does not contain a feaure that lets users subset the historical data by some characteristic (e.g., date, defendant race). The app, however, in principle, could be modified to add that kind of subsetting feature as a step prior to estimating the posterior distribution for bias.

@@

Thank you for this comment.  We have revised the paper accordingly.

@@

Second, we wish to address the idea that a judge may be reluctant to "seriously entertain a Batson challenge" if the strikes in the present case indicate essential equal "removal rates of protected and unprotected members of the venire." As an initial matter, we take "seriously entertain" to denote the premise that judge would be less likely to find a _Batson_ prima facie case and ultimately find a _Batson_ violation, given those removal rates. We do not dispute that premise about judges are likely to do.  We d

>>>>

We have revised accordingly.

@@

We suspect the initial reading arose because "bias" has both a statistical meaning and a conventional meaning, and we are using the latter when referring to $b$ as the bias parameter.

@@

By "cognizable" class, we mean the category to which the struck juror belongs that is the possible basis of strike bias. For example, if the set of prospective jurors consists only of Black and White individuals and the focus is on strike bias _against_ Black prospective jurors because of their race, the "cognizable" class is "Black prospective jurors". If, however, the focus is on strike bias against Black female prospective jurors because of their race and gender, the "cognizable" class is "Black female prospective jurors." We used the phrase "cognizable class members subject to strike" instead of "cognizable class jurors", because at the time any strike occurs, (1) no one is actually a juror, because no one has yet been seated onto the jury, and (2) not every prospective juror could have been struck.

@@

Subsetting the historical data does not necessarily reduce the degree of incompatibility between the historical strike data and the current trial ($b_hist$ - $b_curr$). As we discuss in the paper (page X, lines YY-YY), it depends on what one assumes about how much the subsetting criteria (e.g., only "similar" cases) changes the degree of incompatibility. We stress "assumes", because the true values of $b_hist$ and $b_curr$ are not directly observable in actual cases. Accordingly, for any subset of the historical strike data one chooses, our guidance for choosing an $\alpha$ value remains the same: Check for how sensitive to the posterior estimate of strike bias to different values of $\alpha$. The current version of the software prototype does not let users subset the historical data by some characteristic (e.g., date, defendant race). However, in principle, it could be modified to add that kind of feature.

@@

Thank you for this comment.  We have revised the paper accordingly. [TBD]

@@

Second, we wish to address the idea that a judge may be reluctant to "seriously entertain a Batson challenge" if the strikes in the present case indicate essential equal "removal rates of protected and unprotected members of the venire." we take "seriously entertain" to denote the premise that judge would be less likely to find a _Batson_ prima facie case and ultimately find a _Batson_ violation, given those observed "removal rates". We do not dispute that premise about judge behavior.
